\documentclass[10pt,journal,compsoc]{IEEEtran}

\let\chapter\section

\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fancyhdr}
%\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{color}
\usepackage{url}
%\usepackage{moreverb}
\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{mathptmx}
\usepackage{dingbat}
\usepackage{pifont}
\usepackage{acronym}%
\usepackage{algpseudocode}
%\usepackage{algorithm}
\usepackage{supertabular}
\usepackage{listings}
\usepackage{threeparttable}
\usepackage{enumitem}
\usepackage{pdflscape}
\usepackage{array}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{array}
\usepackage{courier}
\newcommand{\subparagraph}{}
\usepackage{titlesec}

\usepackage{draftwatermark}
\SetWatermarkText{Confidential}
\SetWatermarkScale{0.4}

\usepackage[numbers,sort]{natbib}

\setlist[itemize]{noitemsep, leftmargin=1em}
\setlist[enumerate]{noitemsep, leftmargin=1em}

\lstset{columns=flexible,showstringspaces=false}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{aboveskip=3.3pt,belowskip=3.3pt}

\renewcommand{\algorithmiccomment}[1]{\hfill {\tt //} #1}
\newcommand{\tick}{\ding{52}}
\newcommand{\xmark}{\ding{56}}

\makeatletter
\newcommand{\thickhline}{%
    \noalign {\ifnum 0=`}\fi \hrule height 1pt
    \futurelet \reserved@a \@xhline
}
\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother

\begin{document}

\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications
\newline\newline
\small{\textbf{Response to Review Comments}}}

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2}
Michalis Polychronakis,\IEEEauthorrefmark{3}
and Angelos D. Keromytis\IEEEauthorrefmark{1}}\\
\IEEEauthorblockA{\IEEEauthorrefmark{1}
\scriptsize Department of Computer Scinence,
Columbia University,
\{dimitro, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Department of Management Science and Technology,
Athens University of Economics and Business,
louridas@aueb.gr\\
\IEEEauthorrefmark{3}
Computer Science Department,
Stony Brook University,
mikepo@cs.stonybrook.edu
\vspace{-3mm}
}}

% \markboth{\footnotesize D. Mitropoulos et al.}{\footnotesize Defending Against Web Application Attacks:
% Research Approaches, Challenges and Implications}

\markboth{Response to Review Comments.}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}

\IEEEtitleabstractindextext{
\begin{abstract}
Some of the most dangerous web attacks, such as Cross-Site
Scripting and {\sc sql} injection, exploit vulnerabilities
in web applications that may accept and process
data of uncertain origin without proper validation or
filtering, allowing the injection and execution of
dynamic or domain-specific language code.
These attacks have been constantly topping the lists of
various security bulletin providers despite the numerous
countermeasures that have been proposed over the past 15 years.
In this paper, we provide an analysis on
various defense mechanisms against web code injection attacks.
We propose a model that highlights the key weaknesses enabling these attacks,
and that provides a common perspective for studying the available defenses.
We then categorize and analyze a set of 41 previously proposed defenses 
based on their accuracy, performance,
deployment, security, and availability characteristics.
Detection accuracy is of particular importance,
as our findings show that many defense
mechanisms have been tested in a poor manner. In addition, we observe
that some mechanisms can be bypassed by attackers with knowledge
of how the mechanisms work. Finally, we discuss the results
of our analysis, with emphasis on factors that may hinder
the widespread adoption of defenses in practice.
\vspace{-3mm}
\end{abstract}

\begin{IEEEkeywords}
Web Application Security, Protection Mechanisms, Exploitation Models, Software Testing,
SQL Injection, XSS.
\vspace{-1mm}
\end{IEEEkeywords}}

\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\section{AE Comments}
\label{sec:ae}

{\bf Comment} ``The second and third reviewers
have pointed out problems in missing related work and
descriptions that need to polished.
Please address them carefully in the next revision
for the next round of review."\\

\noindent
{\bf Response:}
We are thankful to the reviewers for their thorough reviews.
We have revised our paper based on their suggestions and comments.
All additions and changes are highlighted in yellow
in the revised manuscript.
In the following we provide answers to specific
comments/suggestions/queries.\\

\section{Reviewer \#1}
\label{sec:r1}

{\bf Comment 1:} ``One downside of this work is that it was not clear from the
description what constitutes a defense against a web application
attack. The authors do say that vulnerability analysis techniques are
out-of-bounds (which I agree with), but what about related
technologies such as Web Application Firewalls? Where does one draw
the line? What are the criteria to evaluate new techniques to see if
they fit into your defenses (so that the authors can evaluate using
your techniques)?"\\

\noindent
{\bf Response:}
In general,
a way to check if a mechanism can be examined
based on our criteria,
is to see if and how it fits into our
exploitation model (point of detection).
Specifically,
application firewalls
fit into our study.
Besides,
in reference~\cite{DPJV06}
the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
that we include in our analysis as
application firewalls.\\

% Such mechanisms though,
% can be seen as host-based application firewalls
% which are different from the network-based
% application firewalls.
% Mechanisms coming from the later category
% operate directly at the application
% layer of the protocol stack and
% in most cases they are modules
% of the web server
% (e.g. {\tt modsecurity})\footnote{\url{https://www.modsecurity.org/}}.
% Even though we do not include such mechanisms
% in our study,
% they can be analyzed based on our criteria.\\
% note: I do not know if we must update the text
% of the paper to address the above comment.

\noindent
{\bf Comment 2:} ``Also, I felt that the focus on
studying ``popular" defenses (those with
greater than 20 citations or published recently) ignores one of the	
main benefits of a survey paper: to help the community discover
overlooked yet quality research. I appreciate that surveying the 35
papers is a good contribution, but I wonder if the results of the
evaluation would be more impactful (in terms of finding overlooked
research) if the survey was more inclusive."\\

\noindent
{\bf Response:}
This is a valid comment.
However,
in order to avoid penalizing recent research,
we have also included recent papers
even though they have been cited less than twenty times.

In addition,
to address the comments of the second
and the third reviewer,
we have extended our study by
including six more mechanisms.
Notably,
one of the mechanisms was presented in a recent
paper with less than 20 citations.
This increases the number of such cases
in our paper (6).\\

\noindent
{\bf Comment 3:} ``Some minor comments for the authors:
\begin{enumerate}
\item Introduction: ``didn't" $\rightarrow$ did not
\item Introduction: ``haven't" $\rightarrow$ have not
\item Section 2: {\sc php} Object Injection vulnerabilities do not have to be
 ``part of cookies". These could come any user input, not necessarily
 cookies (similar to other code injection vulnerabilities).
\item Section 4.5 ``canny attacks" and ``cannier attacker" should probably
 be ``savvy" or a different word.
\item Section 5.1.2 it is not clear from your description that the {\sc csp}
 policy is communicated via {\sc http} header. This may not be clear to
 those readers that aren't familiar with {\sc csp}.
\item Section 5.1.2 ``{\sc xxs}" $\rightarrow$ ``{\sc xss}".
\item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
\end{enumerate}

\noindent
{\bf Response:}
We have updated the text accordingly.\\

\section{Reviewer \#2}
\label{sec:r2}

{\bf Comment 1:} ``The analysis on the accuracy
and performance overhead is not reasonable.
The paper presents metrics that were originally
reported in other papers,
which were evaluated under different
assumptions and settings.
Simply listing the numbers found in those papers
in a table might be misleading.
However,
the reviewer acknowledges that it is very
difficult to have access to those systems for a fair comparison,
and agrees with the recommendation on improving
the availability of the source code and dataset
in future research."\\

\noindent
{\bf Response:}
This is an interesting comment.
We need to mention that we did not intend to
compare the mechanisms with each other
but to analyze and categorize them,
and highlight factors that may hinder
their widespread deployment
(we state this early on in the
``Introduction" section).

Indeed,
the caption of Table 1 actually
started with the phrase ``comparison summary"
which is misleading.
To avoid any further misunderstandings
we have changed the caption of Table 1
to make clear that there
are many different testing setups and
environments for defenses that counter
similar attacks (see Subsection 6.1).\\

\noindent
{\bf Comment 2:} ``Admittedly, transition
from scientific research to real product
is challenging due to availability, usability,
performance and deployment issues.
Except for that, the paper does not thoroughly
discuss why many previous works
cannot stop attacks against web applications,
nor provide useful guidance on
how future research could improve upon existing works.
Are there any fundamental
limitations in previous works that make
them not suitable for defending against
some specific (if not all) attacks?
Can we integrate multiple solutions to build
stronger defense mechanisms?"\\

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms which
combine characteristics
from different categories,
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
they could become more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could employ both {\sc csp}
and \textsc{sql}rand
to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\

\noindent
{\bf Comment 3:} ``Some recent works in the (or related) 
field are not discussed in this paper.
For example, information flow control solutions and
proposals that confine or isolate JavaScript could
be used to defend against code injection attacks.
Examples are: {\sc jsf}low: Tracking information
flow in JavaScript and its {\sc api}s ({\sc sac}'14).
Protecting users by confining JavaScript with {\sc cowl} ({\sc osdi} '14).
Runtime monitoring and formal analysis of information
fows in Chromium ({\sc ndss} '15)."\\

\noindent
{\bf Response:}
We have updated our paper to include the
aforementioned mechanisms
(see Subsection 5.3, Figure 2 and 3).
The 3rd reviewer also
indicated that some representative
{\sc ifc} frameworks were missing.
Hence, we have added those too.
Note that,
those mechanisms are not
always easy to adopt because
developers need to learn new constructs
to utilize them.
We mention that in Subsection 6.4
(``Ease of Use").
Finally,
the addition of {\sc ifc} mechanisms
in our study affects many of our results
throughout Section 6 (``Observations").
Consequently,
we have updated this section too.\\

\section{Reviewer \#3}
\label{sec:r3}

{\bf Comment 1:} ``The biggest omission that I see,
however,
is that the exploitation model does not consider
inter-frame attacks, where an attacker
e.g., lures victims to framed vulnerable
sites and performs cross-frame code
injection.  Granted, this is a relatively
newer update to the pantheon of
web application attacks, but given the rising
prevalence of client-side
web application code it's in my
estimation an important one. 
And,
postMessage
security research dates back to at least the late 2000s,
so it's actually not *that* new."\\

\noindent
{\bf Response:}
Indeed,
Cross Frame Scripting (\textsc{xfs}) attacks
comprise a novel category worth mentioning.
We now describe \textsc{xfs} attacks
in Section 3 (``Exploitation Model").
We also provide a corresponding example.\\

\noindent
{\bf Comment 2:} ``Similarly, {\sc xss} is introduced
as an attack that has two forms,
reflected and persistent.
However,
even though it's mentioned later on,
how would {\sc dom}-based {\sc xss} fit into this breakdown?
I don't believe it does (neatly),
and I am of the view that it constitutes a third
category since it can be performed on-demand
and purely client-side across frames without persistence,
combining aspects of both of the above categories."\\

\noindent
{\bf Response:}
We have updated Section 3 (``Exploitation Model")
to include {\sc dom}-based {\sc xss} attacks
as a the third basic category of {\sc xss}
attacks.\\

\noindent
{\bf Comment 3:} ``Aside from those issues,
one could take issue with a lack of coverage of some
(in my opinion) important approaches that hew towards the
secure-by-construction ideology.
For instance,
there is work from the {\sc pl} community (e.g., Ur/Web)
that makes certain attacks impossible by design.
There is other {\sc pl} work I didn't
see mentioned that also takes a
secure-by-design approach (e.g., {\sc jif}/{\sc sif}).
There is work from the systems
community focused on {\sc difc} (e.g., Hails, Aeolus).
I anticipate that these
wouldn't rate highly on the ease-of-use metrics,
but it would have been nice to see them mentioned.
I did notice that static analyses were specifically
called out as not being in-scope,
but other work that was mentioned does
require application modification (e.g., {\sc js} confinement).
So, while I'm sure there's a line one should draw,
it's not clearly defined here and some of the
above could, in the current presentation,
be considered missing."\\

\noindent
{\bf Response:}
The 2nd reviewer has also indicated that
information flow control solutions
were missing from our study.
Our paper now includes six solutions
that follow this approach,
including {\sc sif}~\cite{CVMA07},
Hails~\cite{GLSTMMR12}
and Aeolus~\cite{CPSPBCCSL12}
(see Subsection 5.3, Figure 2 and 3).
Nevertheless,
we did not include Ur/Web~\cite{C10b}
in our study because it is a static 
analysis mechanism
(recall that we only consider defenses
that prevent attacks when they take place).

Note that,
most of these mechanisms were not
extensively tested in terms of security.
However,
such solutions do not need to be
established purely through testing,
since they provide systematic
arguments as to why their design is
secure against application attacks.
We stress this issue in Subsection
7.1 (``Improving Testing Accuracy").
Furthermore,
we discuss the usability issues of
{\sc ifc} solutions in Subsection 6.4
(``Ease of Use").

As we pointed out in our
response to the 2nd reviewer,
the addition of {\sc ifc} mechanisms
in our paper affects many of our results
throughout Section 6 (``Observations").
Consequently,
we have updated this section too.\\

\bibliographystyle{IEEEtran}
\bibliography{comments}

\end{document} 

